Twists of supersymmetric gauge theories

### 2019-08-26 paper.tex
paper edits

A local functional induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$, see Definition \ref{dfn: fnl} in the appendix. 
The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
\begin{equation}\label{bvcplx}
\left(\cO(\cE), Q + \{I,-\}\right) .
\end{equation}
In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
We will refer to this as the {\bf classical BV complex} of the theory.

@@

Note that a map of classical field theories induces a map of BV complexes, that is, a map of pro-cochain complexes:
\[
F^*\colon \left(\cO (\cE)[-1], Q + \{I,-\} \right) \to \left(\cO (\cE')[-1], Q' + \{I',-\} \right) .
\]
This allows us to make the following definition of an equivalence between classical theories.

@@

We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes (see Appendix \ref{appx:infinity}).

Concretely, an action of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
\[\sum_{k\geq 1} I^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
which satisfies the Maurer--Cartan equation
\[\{S_{\mr{BV}}, I^{(k+1)}\} + \d_{CE} I^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I^{(a)}, I^{(b)}\} = 0\]
for every $k\geq 0$.

@@

%\begin{landscape}
\begin{figure}
\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
\node (825) [right=of 82] {};
\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};

\draw[arrow] (101) -- (91);
\draw[arrow] (91) -- (81);
\draw[arrow] (91) -- (82);
\draw[arrow] (81) -- (71);
\draw[arrow] (82) -- (71);
\draw[arrow] (82) -- (72);
\draw[arrow] (83) -- (73);
\draw[arrow] (71) -- (61);
\draw[arrow] (71) -- (62);
\draw[arrow] (72) -- (62);
\draw[arrow] (72) -- (63);
\draw[arrow] (73) -- (65);
\draw[arrow] (61) -- (51);
\draw[arrow] (62) -- (51);
\draw[arrow] (62) -- (52);
\draw[arrow] (63) -- (53);
\draw[arrow] (64) -- (52);
\draw[arrow] (64) -- (54);
\draw[arrow] (65) -- (54);
\draw[arrow] (51) -- (41);
\draw[arrow] (51) -- (42);
\draw[arrow] (52) -- (42);
\draw[arrow] (52) -- (43);
\draw[arrow] (53) -- (43);
\draw[arrow] (54) -- (43);
\draw[arrow] (54) -- (44);
\draw[arrow] (54) -- (45);
\draw[arrow] (41) -- (31);
\draw[arrow] (42) -- (31);
\draw[arrow] (42) -- (32);
\draw[arrow] (43) -- (32);
\draw[arrow] (44) -- (32);
\draw[arrow] (45) -- (32);
\draw[arrow] (31) -- (21);
\draw[arrow] (31) -- (22);
\draw[arrow] (32) -- (22);

\node (2d) [dimension, left=of 21] {2d};
\node (3d) [dimension, above=of 2d] {3d};
\node (4d) [dimension, above=of 3d] {4d};
\node (5d) [dimension, above=of 4d] {5d};
\node (6d) [dimension, above=of 5d] {6d};
\node (7d) [dimension, above=of 6d] {7d};
\node (8d) [dimension, above=of 7d] {8d};
\node (9d) [dimension, above=of 8d] {9d};
\node (10d) [dimension, above=of 9d] {10d};
\end{tikzpicture}
\caption{Orbits of square-zero supercharges.}
\label{fig:superchargeorbits}
\end{figure}
%\end{landscape}

>>>>

A local functional $I$ induces an endomorphism $\{I,-\}$ on the space of all local functionals $\oloc(E)$. 
It also induces an endomorphism on the larger space of {\em all} functionals $\cO(\cE)$\footnote{Although, for two arbitrary functionals $F, G \in \cO(\cE)$, the bracket $\{F,G\}$ is not defined.}, see Definition \ref{dfn: fnl} in the appendix. 
The classical master equation implies that the operator $Q + \{I,-\}$ squares to zero on $\cO(\cE)$, and hence every classical field theory defines a cochain complex
\begin{equation}\label{bvcplx}
\left(\cO(\cE), Q + \{I,-\}\right) .
\end{equation}
In fact, this has the structure of a differentiable pro-cochain complex, see Definition \ref{dfn: pro}. 
We will refer to this as the {\em classical BV complex} of the theory.

@@

Note that a map of classical field theories induces a map of BV complexes, that is, a map of pro-cochain complexes:
\[
F^*\colon \left(\cO (\cE')[-1], Q' + \{I',-\} \right) \to \left(\cO (\cE)[-1], Q + \{I,-\} \right).
\]
This allows us to make the following definition of an equivalence between classical theories.

@@

We denote components of an $\infty$-morphism by $\rho_2, \rho_3, \dots$, so that $\rho_2$ is a morphism of (super) chain complexes (see Appendix \ref{appx:infinity}).
\brian{Is there a reason $\rho_2$ is the linear map. I'd thought $\rho_1$...}

Concretely, an action $\rho$ of a super dg Lie algebra $\fg$ on a classical field theory is given by an element
\[I_{\rho} = \sum_{k\geq 1} I_{\rho}^{(k)}\in \oloc(E)\otimes \widehat{\sym}^{\geq 1}(\fg^*[-1])\]
which satisfies the Maurer--Cartan equation
\[\{S_{\mr{BV}}, I_\rho^{(k+1)}\} + \d_{CE} I_{\rho}^{(k)} + \frac{1}{2}\sum_{a+b=k+1} \{I_{\rho}^{(a)}, I_{\rho}^{(b)}\} = 0\]
for every $k\geq 0$.

@@

%%\begin{landscape}
%\begin{figure}
%\begin{tikzpicture}[node distance=0.35cm and 0.35cm, text width=1.8cm]
%\node (101) [s16chiral] {Rank $(1, 0)$ $d=5$};
%\node (91) [s16, below=of 101] {Rank $1$ $d=5$};
%\node (82) [s16, below=of 91] {Rank $(1, 1)$ $d=5$};
%\node (81) [s16, left=of 82] {Rank $(1, 0)$ $d=4$};
%\node (825) [right=of 82] {};
%\node (83) [s16, right=of 825] {Rank $(1, 0)$ $d=8$};
%\node (71) [s16, below=of 81] {Rank $1$ $d=4$};
%\node (72) [s16, below=of 82] {Rank $2$ $d=5$};
%\node (73) [s16, below=of 83] {Rank $1$ $d=7$};
%\node (62) [s16, below=of 71] {Rank $(1, 1)$ $d=4$};
%\node (61) [s8, left=of 62] {Rank $(1, 0)$ $d=3$};
%\node (63) [s16, below=of 72] {Rank $(2, 2)$ $d=5$};
%\node (64) [s16chiral, right=of 63] {Rank $(2, 0)$ $d=5$};
%\node (65) [s16, below=of 73, right=of 64] {Rank $(1, 1)$ $d=6$};
%\node (51) [s8, below=of 61] {Rank $1$ $d=3$};
%\node (52) [s16, below=of 62] {Rank $2$ $d=4$};
%\node (53) [s16, below=of 63] {Rank $4$ $d=5$};
%\node (54) [s16, below=of 64] {Rank $2$ $d=5$};
%\node (42) [s8, below=of 51] {Rank $(1, 1)$ $d=3$};
%\node (41) [s4, left=of 42] {Rank $(1, 0)$ $d=2$};
%\node (43) [s16, right=of 42] {Rank $(2, 2)$ $d=4$};
%\node (44) [s16, right=of 43] {Rank $(2, 1)$ $d=4$};
%\node (45) [s8, right=of 44] {Rank $(2, 0)$ $d=4$};
%\node (31) [s4, below=of 41] {Rank $1$ $d=2$};
%\node (32) [s8, below=of 42] {Rank $2$ $d=3$};
%\node (22) [s4, below=of 31] {Rank $(1, 1)$ $d=2$};
%\node (21) [s2chiral, left=of 22] {Rank $(1, 0)$ $d=1$};
%
%\draw[arrow] (101) -- (91);
%\draw[arrow] (91) -- (81);
%\draw[arrow] (91) -- (82);
%\draw[arrow] (81) -- (71);
%\draw[arrow] (82) -- (71);
%\draw[arrow] (82) -- (72);
%\draw[arrow] (83) -- (73);
%\draw[arrow] (71) -- (61);
%\draw[arrow] (71) -- (62);
%\draw[arrow] (72) -- (62);
%\draw[arrow] (72) -- (63);
%\draw[arrow] (73) -- (65);
%\draw[arrow] (61) -- (51);
%\draw[arrow] (62) -- (51);
%\draw[arrow] (62) -- (52);
%\draw[arrow] (63) -- (53);
%\draw[arrow] (64) -- (52);
%\draw[arrow] (64) -- (54);
%\draw[arrow] (65) -- (54);
%\draw[arrow] (51) -- (41);
%\draw[arrow] (51) -- (42);
%\draw[arrow] (52) -- (42);
%\draw[arrow] (52) -- (43);
%\draw[arrow] (53) -- (43);
%\draw[arrow] (54) -- (43);
%\draw[arrow] (54) -- (44);
%\draw[arrow] (54) -- (45);
%\draw[arrow] (41) -- (31);
%\draw[arrow] (42) -- (31);
%\draw[arrow] (42) -- (32);
%\draw[arrow] (43) -- (32);
%\draw[arrow] (44) -- (32);
%\draw[arrow] (45) -- (32);
%\draw[arrow] (31) -- (21);
%\draw[arrow] (31) -- (22);
%\draw[arrow] (32) -- (22);
%
%\node (2d) [dimension, left=of 21] {2d};
%\node (3d) [dimension, above=of 2d] {3d};
%\node (4d) [dimension, above=of 3d] {4d};
%\node (5d) [dimension, above=of 4d] {5d};
%\node (6d) [dimension, above=of 5d] {6d};
%\node (7d) [dimension, above=of 6d] {7d};
%\node (8d) [dimension, above=of 7d] {8d};
%\node (9d) [dimension, above=of 8d] {9d};
%\node (10d) [dimension, above=of 9d] {10d};
%\end{tikzpicture}
%\caption{Orbits of square-zero supercharges.}
%\label{fig:superchargeorbits}
%\end{figure}
%%\end{landscape}
